Death By Dropdown?

### 2025-04-07 conference-materials/2025_shiny-conf/slides.qmd
Refines BID framework description
- Enhances explanation of BID by emphasizing systematic integration of behavioral science and its unique approach beyond checklists.
- Clarifies how BID connects psychological principles to coding decisions, aiding developers in applying theory effectively.

Process-oriented framework vs. broad checklist approach
:::

@@

- "BID integrates existing best practices from multiple disciplines"..."We're truly standing on the shoulders of giants here"
  * Click through example fields...UX, data storytelling, psych science, data/visual communication
- Key differentiator: "But what makes BID unique is its process-oriented framework vs. a typical checklist approach"
- "The goal is helping users gain clearer insights while giving developers a tool to use in their workflows"
- "Even though there's a lot of theory, you don't need a psychology degree to apply these principles effectively"
- "To demonstrate...let's take a closer look at how we connected these stages to SoundPulse's dashboard."
:::

>>>>

Systematic integration of behavioral science within the natural dashboard development workflow
:::

@@

- "BID integrates existing best practices from multiple disciplines"..."We are truly standing on the shoulders of giants here"
  * Click through example fields...UX, data storytelling, psych science, data/visual communication
- Key differentiator: "But what makes BID uniquely powerful is how it systematically connects psychological principles to specific coding decisions at each stage of development"
- "Unlike checklists that tell you what to do, BID guides how you think about your dashboard from psychological first principles"
- "The framework bridges theory and practice - showing not just what principles matter, but exactly when and how to apply them in your development workflow"
- "Even though there's a lot of theory, you don't need a psychology degree to apply these principles effectively"
- "To demonstrate...let's take a closer look at how we connected these stages to SoundPulse's dashboard."
:::
